---
title: A0 solution - Rmarkdown First Lab
author: |
  | Last name: Khambaita
  | First name: Sunil
  | Student ID: 1000285924
  | Course section: STA302H1F-L0101
date: "Sept. 21th, 2016"
output: pdf_document
fontsize: 10pt
---
# Q3 - Plot cars data

### 3.1. Cars data

We'll look at data frame and plotting in much more detail in later classes.  For a previous of what's to come, here's a very basic example.

For this example we'll use a very simple dataset.  The `cars` data comes with the default installation of R.  To see the first few columns of the data, just type `head(cars)`.

```{r}
head(cars)
```

We'll do a bad thing here and use the `attach()` command, which will allow us to access the `speed` and `dist` columns of `cars` as though they were vectors in our workspace.

```{r}
attach(cars) # Using this command is poor style.  We will avoid it in the future.
```

We can easily produce a histogram of stopping distance using the `hist` function.
```{r}
hist(dist) # Histogram of stopping distance
```

