---
title:  Visualizing Data Using ggplot2
author: |
  | Last name: Khambaita
  | First name: Sunil
  | Student ID: 1000285924
  | Course section: STA303H1S-L0101
date: "Jan 2nd, 2017"
output: pdf_document
fontsize: 10pt
---

# \textcolor{blue}{ Q1 - Factor variables analysis}

\textbf{Question: (1 point)} How many factor variables in this data set? Use R command \textit{str(diamonds)} to find it. For each factor variable, find the one-way frequency table for it. An example of cut variable is given in the solution template.

\textbf{Answer}: We have 3 factor varibles. They are cut (with 5 levels), color (with 7 levels) and clarity (with 8 levels).

```{r,echo=TRUE,eval=TRUE,warning=FALSE}

# Installing ggplot2 R packages
# install.packages("ggplot2") <--- I ready installed it, hence commented out.

# Loading gg2plot2 and reading in diamonds data
library(ggplot2)
data(diamonds)

# check the type of variables in this data
str(diamonds)

# observations for each level of "cut" variable
table(diamonds$cut) # or summary(diamonds$cut)
```
\newpage

```{r,echo=TRUE,eval=TRUE,warning=FALSE}
# find the level frequency of "cut" varible
prop.table( table(diamonds$cut) ) # or summary(diamonds$cut)/nrow(diamonds)

# find the level frequency of "color" varible 
prop.table( table(diamonds$color) ) 

# find the level frequency of "clarity" varible
prop.table( table(diamonds$clarity) )
```
\newpage 

# \textcolor{blue}{ Q2 -Produce plot and give comment}

## Scatter plot 

```{r,echo=TRUE,eval=TRUE, warning=FALSE}
# Loading the ggplot2 library
library(ggplot2)

# Reading in the data file
data(diamonds)

# Creating a ggplot
myplot <- ggplot(diamonds, aes(x = carat, y = price, color = clarity)) + geom_point()

# print the plot
myplot
```

## Comments: 
There is few things to observe from just looking at this graph:  
- We notice that the clearer the diamond (clarity) the higher the price.  
- We notice that the heavier the diamond (carat) the higher the price.  
- We notice that as the heavier the diamond gets (carat), the less likely we are to find it being of the highest clarity. As we can see from 3 carats and above, there's mainly SI2 and I1 clarity type diamonds available.  

